---
title: The Impact of Weather on Flight Delay
author:
  - name: MyName
    email: johndoe@corps.com
    affiliations:
      - Random University
  - name: No Name
    affiliations:
      - Highest-ranked University
date: "`r Sys.Date()`"
abstract: |
  This is a sample article for illustrating how to write a reproducible research article using R and Quarto. `preamble.tex` is used to set up the LaTeX environment, such as packages and custom commands. `title.tex` (in the template folder) is used to customize the title page. `american-journal-of-agricultural-economics.csl` is the citation style for AJAE. It can be downloaded from https://github.com/citation-style-language/styles. The `template` folder contains these three files. `bibliography.bib` is the bibliography file
bibliography: bibliography.bib
csl: ./template/american-journal-of-agricultural-economics.csl 

format: 
  pdf:
    number-sections: true
    keep-tex: false # set to true if you want to keep the intermediate .tex file
    fontfamily: times
    tbl-cap-location: top
    include-in-header: 
      - ./template/preamble.tex # preamble.tex is used to set up the LaTeX environment, such as packages and custom commands
    template-partials: 
      - ./template/title.tex # title.tex is used to customize the title page

execute: 
  echo: false
  message: false
  warning: false
---


```{r}
#| label: setup
#| include: FALSE

# --- load packages --- #
pacman::p_load(officer, modelsummary, data.table, dplyr, ggplot2)

# --- prepare results --- #
# You can directly load the R objects created in a different qmd file using the following code. Then, you can use the loaded objects (data, figure, table, etc.) in the current qmd file.
# knitr::knit_child("../code/2_make_tables_figures.qmd", quiet = TRUE)
```


# Introduction

Nothing is more frustrating than flight delays. The goal of this article is to understand what weather variables affect flights delays so that we can control weather when such time comes in the future[^1].

[^1]: This is just for illustrating how to create a footnote

# Method

Regression analysis was used in this article. The econometric model writes as follows (Equation \ref{econometric-model}):

\begin{align}
y_{i,t} = \beta_0 + \beta_1 temp_{i,t} + \beta_2 precip_{i,t} + \beta_3 wind_speed_{i,t} + v_{i,t} \label{econometric-model}
\end{align}

## Code availability

All computations (including creating tables and plots) were conducted using R software [@R], The @fixest package was used to run regressions.

# Data

We use publicly available datasets from the R `nycflights13` package [@nycflights13]. @tbl-sum-stat presents the summary statistics.

```{r}
#| label: tbl-sum-stat
#| tbl-cap: Summary Statistics

reg_data <- readRDS("../data/processed/reg_data.rds")
# Or, you can also use the following code to read the data, which is more robust to changes in the working directory.
# reg_data <- readRDS(here::here("data/processed/reg_data.rds"))


datasummary(
  dep_delay + temp + precip + wind_speed ~ Mean + SD + Max, 
  data = reg_data
)
```

@fig-hist-delay shows the histogram of departure delay by carrier for each of the airports. 

```{r}
#| label: fig-hist-delay
#| fig-cap: Distribution of delay by carrier

knitr::include_graphics("../results/figures/delay_box.pdf")
```

# Results and Discussions

@tbl-reg-results presents the regression results.

```{r}
#| label: tbl-reg-results
#| tbl-cap: Regression Results

# --- load a list of regression results --- #
ls_reg_results <- readRDS("../results/reg_results.rds")

# --- create regression results table --- #
reg_table <-
  modelsummary(
    models = ls_reg_results, 
    coef_map = c(
      "temp" = "Temperature",
      "precip" = "Precipitation",
      "wind_speed" = "Wind Speed"
    ),
    stars = TRUE,
    gof_omit = "IC|Log|Adj|F|Pseudo|Within|RMSE"
  )

reg_table
```

# Conclusion

Weather matters.

\newpage

# References {-}

::: {#refs}
:::
