# Objective

This document explains how to reproduce all main outputs of the project, including data preparation, empirical analysis, tables, figures, and the final manuscript.

# Before you start

To reproduce this project, you need:

- R
- Quarto
- all project files in their original folder structure

The following R packages are required to run the code in this project. Run the code below, which will automatically install any missing packages and load all the required packages.

```{r}
#| eval: FALSE

if(!require("pacman")) install.packages("pacman")

pacman::p_load(
  here,
  rio,
  quarto,
  data.table,
  dplyr,
  fixest,
  ggplot2,
  ggtext,
  flextable,
  modelsummary
)
```


# Reproducing the project

The following code runs the full workflow for this project:

1. Process the raw data (`code/0_process_data.qmd`)
2. Run the regression analysis (`code/1_reg_analysis.qmd`)
3. Create tables and figures (`code/2_make_tables_figures.qmd`)
4. Render the manuscript (`writing/manuscript_to_word.qmd` and `writing/manuscript_to_pdf.qmd`)

Each step depends on outputs from earlier steps, so the workflow must be executed in this order.

```{r}
quarto_render(here("code/0_process_data.qmd"))

quarto_render(here("code/1_reg_analysis.qmd"))

quarto_render(here("code/2_make_tables_figures.qmd"))

quarto_render(here("writing/manuscript_to_pdf.qmd"))
```

In addition, each `.qmd` file produces an `.html` output, which serves as an easily readable record of the process and results.
