# Objective

This document explains how to reproduce all main outputs of the project, including data preparation, empirical analysis, tables, figures, and the final manuscript.

# Before you start

To reproduce this project, you need:

- R
- Quarto
- the `renv` package
- all project files in their original folder structure

The following R packages are required to run the code in this project. Run the code below to install them if you haven't already.

```{r}
#| eval: FALSE

if(!require("pacman")) install.packages("pacman")

pacman::p_load(
  here,
  rio,
  quarto,
  data.table,
  dplyr,
  ggplot2,
  ggtext,
  flextable,
  modelsummary
)
```


# Implement the project

The following code runs the full workflow for this project:

1. Process the raw data (code/0_process_data.qmd)
2. Run the regression analysis (code/1_reg_analysis.qmd)
3. Create tables and figures (code/2_make_tables_figures.qmd)
4. Render the manuscript (writing/manuscript_to_word.qmd and writing/writing_to_pdf.qmd)

```{r}
quarto::quarto_render(here::here("code/0_process_data.qmd"))

quarto::quarto_render(here::here("code/1_reg_analysis.qmd"))

quarto::quarto_render(here::here("code/2_make_tables_figures.qmd"))

quarto::quarto_render(here("writing/manuscript_to_word.qmd"))
```

